An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-17 VLDB2026/main.tex
change

@@

	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them. This means that DSG is more sensitive to changes in data distribution. 
	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets. As shown in Figure~\ref{fig:exp_8_3}, the performance differences. All methods perform worst on WIT, which has the highest LID. On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance. 
	%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
	%	
	%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID. This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.

>>>>

	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.332\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/attribute_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}

		\caption{\textcolor{violet}TrinityExtension——Attribution}
		\label{fig:TrinityExtension——Attribution}
	\end{figure}

@@

	However, even though Deep and YT-Audio have similar LID values, the DSG algorithm shows large performance differences between them. This means that DSG is more sensitive to changes in data distribution. 
	%	Its robustness is lower than that of other methods, possibly because it depends not only on LID but also on other complex data characteristics.
	%	To examine the robustness of RF-ANNS algorithms, we analyze their performance across different datasets. As shown in Figure~\ref{fig:exp_8_3}, the performance differences. All methods perform worst on WIT, which has the highest LID. On Deep and YT-Audio, which have similar LID, most algorithms achieve comparable performance. 
	%	This suggests that the effectiveness of RF-ANN search is mainly influenced by LID of the dataset. A higher LID inherently increases the difficulty of hybrid query.
	%	
	%	However, the DSG algorithm shows a noticeable performance gap between the Deep and YT-Audio datasets, despite their comparable LID. This indicates that DSG is less robust than other methods when facing dataset-dependent variations, possibly due to its sensitivity to data distribution beyond LID alone.
	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/exp/range_legend.pdf}

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.332\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/exp/range_multimodel.pdf}
			\caption{\footnotesize MultiModel}
			\label{fig:MultiModel range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer range}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.315\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/range_deep100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset range}
		\end{subfigure}

		\caption{\textcolor{red}TrinityExtension——Range}
		\label{fig:TrinityExtension——Range}
	\end{figure}
